### 2017-12-30 article.tex
add appendix

\section{Conclusion}

\newpage

\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}

>>>>

\section{Conclusion}
The Company had a better financial year in 2016 than 2015. Its turnover grew estimate 43.5 percent. Despite the high increase in revenue, JD still suffered net loss in 2016. The main reason of JD’s negative profit is the high expenses. Cost of revenue was more than 80\% in both 2015 and 2016, which accounted for its negative profit. Another expense is fulfillment which accounted for nearly 10\% of its expenses. In spite of the fact that JD suffered annual losses since it listed, it enlarged its market share as online retailer. Its managements also show strong confidence to their ability to further increase and leverage their scale of business.

Honestly speaking, JD’s strategy of optimizing customer experience and achieving customer satisfaction achieved great success in building its goodwill and establish its market. Continually increasing in revenue reflects recognition of customers to its low price and high quantity of service. After searching JD’s annual report in 2017, we find the Group made a large amount of profit as a result of it previous accumulation.

It is worth mention that though JD suffered net loss in successive years, it did not break down. Due to its strong financing capacity and a positive cash provided by operating activities, JD could still operate in good conditions. Its cooperation with Tencent also enlarged its ability of raising money.
However, from the investors’ point of view, buying JD’s shares is risky. On the one hand, JD has never declared a dividend since it listed. On the other hand, JD has been subject to negative profit for nearly 12 years, which resulted in a negative EPS every year. Although JD’s asset scale increased every year, it is worrying that whether successive loss would influence the price of shares.

There are also some good reasons for investors to buy JD’s shares. Considering the high-speed development of e-commerce, companies like JD which manipulate large amount of market share and has a good reputation has a bright future of development. JD’s operating activities and financing activities also showed its capacity to raise adequate money to maintain its daily operation and further investments.

From JD’s point of view, the company’s strategy in recent years was rather correct. It was shown in the report that JD put most of its money in expanding its scale and grab market share with other online retailers. After a long and vigorous investment, it is believed that the company has the ability to make great profit in the near future.

Nevertheless, the company should also attach great importance to its expenses. In order to attract customers, JD sales at a very low price, resulting in small profit in its main business. Thus, to obtain a positive profit, the company must reduce its expenses.

On the whole, JD is lost in new business expansion and investment, but its layout will remain competitive for a long time in the future. So far, JD has successfully established its retail and financial systems. Meanwhile, sufficient cash flow also provides the foundation for its future development. In the latest quarterly report, we can find that JD has turn loss into profits. Due to these conditions, JD’s share is worth buying as a long-term investment.

\newpage
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}

\includepdf[pages=-]{appendix.pdf} 
\newpage
